Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-05-29 paper-amia-2018/manuscript.tex
update ROC figures

%When lexical features are used in combination with punctuation mark and topic model-based features, recall increases by 0.6\%, 2.5\%, and 11.92\%; and F1-measure increases by 0\%, 3.39\%, and 7\% for NB, SVM, and KNN models, respectively, while precision increases by 4.31\% and 1.49\% for SVM and KNN methods and decreases by 0.7\% for NB. \\

@@

In this paper, results are reported by each class to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall and F1-measure were used to eliminate doubt about the model performance since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. Although NB provides lowest classification results, it shows the second highest AUC values, achieving 0.978 AUC when only lexical features are used and 0.977 AUC when a combination of lexical, punctuation and topic features are used. On the other hand, KNN and SVM exhibit 0.972 and 0.833 AUCs when only lexical features are used; and 0.966 and 0.922 AUCs when a combination of lexical, punctuation and topic model-based features are used. Finally, LSTM demonstrates the highest AUC value among all machine learning models, achieving 0.998 AUC, while GRU achieves only 0.2\% lower AUC than LSTM.

%The conclusion drawn from the ROC curves also confirmed the robustness and superiority of KNN model for the segmentation of clinical exchange.

@@

%We also plan to use more relevant features to improve model performance. For example, part-of-speech tagging\cite{hasan2016feedback} and distance from %the beginning and end of the current sentence might significantly enhance the classification performance.

>>>>

@@

In this paper, results are reported by each class to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall and F1-measure were used to eliminate doubt about the model performance since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. Although NB provides lowest classification results, it shows the second highest AUC values, achieving 0.978 AUC when only lexical features are used and 0.977 AUC when a combination of lexical, punctuation and topic features are used. On the other hand, KNN and SVM exhibit 0.972 and 0.833 AUCs when only lexical features are used; and 0.966 and 0.922 AUCs when a combination of lexical, punctuation and topic model-based features are used. Finally, LSTM demonstrates the highest AUC value among all machine learning models, achieving 0.996 AUC, while GRU achieves only 0.4\% lower AUC than LSTM.

@@
